---
title: "Calculate sample CWMD"
output: html_document
date: "2022-09-30"
---

## Description
This Rmd uses pre-trained w2v model to get concept word mover's distance between each article and the centroid of each perspective. 

## Inputs

-> models_storage/w2v_models/w2v_model_1103.bin
-> dataframes of sample of 20 articles for each perspective (neg_cult_sample_wmd_cos.csv and similar csv's)
-> core seed terms for each perspective

## Outputs
-> dataframes of articles with cwmd scores (pos_cult_sample_cwmd_df.csv and similar csv's) (later processed and normalized in Calculate_WMD_cos_scores_full.ipynb. For full sample, just use full df (i.e. neg_cult_full_wmd_cos.csv). 
  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r pressure, echo=FALSE}

library(reticulate)
```

```{r}
library(word2vec)
```

```{r}
library(word2vec)

```

```{r}
library(text2map)
```

```{r}
library(text2vec)
```



```{r}
neg_cult_sample = read.csv('/Users/nancyxu/wmd/neg_cult_sample_wmd_cos.csv')
pos_cult_sample = read.csv('/Users/nancyxu/wmd/pos_cult_sample_wmd_cos.csv')

neg_rela_sample = read.csv('/Users/nancyxu/wmd/neg_rela_sample_wmd_cos.csv')
pos_rela_sample = read.csv('/Users/nancyxu/wmd/pos_cult_sample_wmd_cos.csv')

neg_dem_sample = read.csv('/Users/nancyxu/wmd/neg_demog_sample_wmd_cos.csv')
pos_dem_sample = read.csv('/Users/nancyxu/wmd/pos_demog_sample_wmd_cos.csv')
```

```{r}
library('quanteda')
```

## get document-feature matrix for each sample dataframe

```{r}
dfmat_neg_cult <- dfm(tokens(neg_cult_sample[,'processed'],
                remove_punct = TRUE))

head(dfmat_neg_cult)
```


```{r}
dfmat_pos_cult <- dfm(tokens(pos_cult_sample[,'processed'],
                remove_punct = TRUE))

head(dfmat_pos_cult)
```


```{r}
dfmat_neg_rela <- dfm(tokens(neg_rela_sample[,'processed'],
                remove_punct = TRUE))

head(dfmat_neg_rela)
```



```{r}
dfmat_pos_rela <- dfm(tokens(pos_rela_sample[,'processed'],
                remove_punct = TRUE))

head(dfmat_pos_rela)
```


```{r}
dfmat_neg_dem <- dfm(tokens(neg_dem_sample[,'processed'],
                remove_punct = TRUE))

head(dfmat_neg_dem)
```


```{r}
dfmat_pos_dem <- dfm(tokens(pos_dem_sample[,'processed'],
                remove_punct = TRUE))

head(dfmat_pos_dem)
```

## load w2v model & get embedding matrix

```{r}
library(word2vec)
model=read.word2vec('/Users/nancyxu/Downloads/w2v_model_1103.bin')
```



```{r}
emb <- as.matrix(model)
```

```{r}
dem.seed <- c('age dependence',
 'birth rate',
 'carrying capacity',
 'chance survival',
 'competition',
 'death rate',
 'density',
 'ecological',
 'ecology',
 'evolution',
 'evolutionary',
 'failure rate',
 'fitness',
 'founding rate',
 'generalism',
 'generalist',
 'inertia',
 'inertial',
 'legitimacy',
 'legitimate',
 'legitimation',
 'liability newness',
 'natural selection',
 'niche',
 'organizational form',
 'population',
 'population ecology',
 'reliability',
 'resistance change',
 'selection',
 'selection',
 'size dependence',
 'specialism',
 'specialist',
 'structural inertia',
 'survival chance')
```


```{r}
rela.seed <- c('board directors',
 'buffer',
 'coalition',
 'constrain',
 'constraint',
 'control',
 'cooperate',
 'cooperation',
 'coopt',
 'cooptation',
 'dependence',
 'dependent',
 'director interlock',
 'director interlocks',
 'diversification',
 'diversify',
 'dominance',
 'exchange',
 'external',
 'horizontal',
 'influence',
 'interdependence',
 'interdependent',
 'interlock',
 'interlocking',
 'joint venture',
 'merge',
 'merged',
 'merger',
 'network',
 'network',
 'power',
 'pressure',
 'resource dependence',
 'sanction',
 'vertical')
```

```{r}
cult.seed <- c('ceremonial',
 'coercion',
 'coercive',
 'conform',
 'conformity',
 'cultural',
 'decouple',
 'decoupled',
 'diffuse',
 'diffusion',
 'imitate',
 'imitation',
 'innovation',
 'institutional',
 'institutionalize',
 'institutionalize',
 'interorganizational field',
 'isomorphic',
 'isomorphism',
 'legitimacy',
 'legitimate',
 'legitimation',
 'loosely coupled',
 'mimetic',
 'norm',
 'normative',
 'norms',
 'organizational field',
 'profession',
 'professional',
 'rationalize',
 'rationalized',
 'ritual',
 'socially constructed',
 'structuration',
 'taken granted')
```



## check which seed terms are in the vocab

```{r}
v <- rownames(emb)
```


```{r}
check = c()
for (i in rela.seed){
  if (i %in% v){
    print(i)
  }
  
}
```

```{r}
check = c()
for (i in cult.seed){
  if (i %in% v){
    print(i)
  }
  
}
```

```{r}
check = c()
for (i in dem.seed){
  if (i %in% v){
    print(i)
  }
  
}
```


## get concept mover's distance for each sample dataframe with the centroid of each perspective's seed terms

```{r}




dem.seed <- c(
 
 'competition',

 'density',
 'ecological',
 'ecology',
 'evolution',
 'evolutionary',

 'fitness',

 'generalism',
 'generalist',
 'inertia',
 'inertial',
 'legitimacy',
 'legitimate',
 'legitimation',


 'niche',

 'population',

 'reliability',

 'selection',
 'selection',

 'specialism',
 'specialist')

```


```{r}



rela.seed <- c(
 'buffer',
 'coalition',
 'constrain',
 'constraint',
 'control',
 'cooperate',
 'cooperation',
 'coopt',
 'cooptation',
 'dependence',
 'dependent',
 
 'diversification',
 'diversify',
 'dominance',
 'exchange',
 'external',
 'horizontal',
 'influence',
 'interdependence',
 'interdependent',
 'interlock',
 'interlocking',

 'merge',
 'merged',
 'merger',
 'network',
 'network',
 'power',
 'pressure',

 'sanction',
 'vertical')


```



```{r}



cult.seed <- c('ceremonial',
 'coercion',
 'coercive',
 'conform',
 'conformity',
 'cultural',
 'decouple',
 'decoupled',
 'diffuse',
 'diffusion',
 'imitate',
 'imitation',
 'innovation',
 'institutional',
 'institutionalize',
 'institutionalize',

 'isomorphic',
 'isomorphism',
 'legitimacy',
 'legitimate',
 'legitimation',

 'mimetic',
 'norm',
 'normative',
 'norms',

 'profession',
 'professional',
 'rationalize',
 'rationalized',
 'ritual',

 'structuration',
 'taken granted')

```




```{r}
pos_cult.sc <- get_centroid(cult.seed, emb)
pos_rela.sc <- get_centroid(rela.seed, emb)
pos_dem.sc <- get_centroid(dem.seed, emb)

pos_cult_dist_centroid_with_cult_seed = CMDist(dtm = dfmat_pos_cult, cv = pos_cult.sc, wv = emb)
pos_cult_dist_centroid_with_rela_seed = CMDist(dtm = dfmat_pos_cult, cv = pos_rela.sc, wv = emb)
pos_cult_dist_centroid_with_dem_seed = CMDist(dtm = dfmat_pos_cult, cv = pos_dem.sc, wv = emb)

neg_cult_dist_centroid_with_cult_seed = CMDist(dtm = dfmat_neg_cult, cv = pos_cult.sc, wv = emb)
neg_cult_dist_centroid_with_rela_seed = CMDist(dtm = dfmat_neg_cult, cv = pos_rela.sc, wv = emb)
neg_cult_dist_centroid_with_dem_seed = CMDist(dtm = dfmat_neg_cult, cv = pos_dem.sc, wv = emb)


pos_dem_dist_centroid_with_cult_seed = CMDist(dtm = dfmat_pos_dem, cv = pos_cult.sc, wv = emb)
pos_dem_dist_centroid_with_rela_seed = CMDist(dtm = dfmat_pos_dem, cv = pos_rela.sc, wv = emb)
pos_dem_dist_centroid_with_dem_seed = CMDist(dtm = dfmat_pos_dem, cv = pos_dem.sc, wv = emb)

neg_dem_dist_centroid_with_cult_seed = CMDist(dtm = dfmat_neg_dem, cv = pos_cult.sc, wv = emb)
neg_dem_dist_centroid_with_rela_seed = CMDist(dtm = dfmat_neg_dem, cv = pos_rela.sc, wv = emb)
neg_dem_dist_centroid_with_dem_seed = CMDist(dtm = dfmat_neg_dem, cv = pos_dem.sc, wv = emb)

pos_rela_dist_centroid_with_cult_seed = CMDist(dtm = dfmat_pos_rela, cv = pos_cult.sc, wv = emb)
pos_rela_dist_centroid_with_rela_seed = CMDist(dtm = dfmat_pos_rela, cv = pos_rela.sc, wv = emb)
pos_rela_dist_centroid_with_dem_seed = CMDist(dtm = dfmat_pos_rela, cv = pos_dem.sc, wv = emb)

neg_rela_dist_centroid_with_cult_seed = CMDist(dtm = dfmat_neg_rela, cv = pos_cult.sc, wv = emb)
neg_rela_dist_centroid_with_rela_seed = CMDist(dtm = dfmat_neg_rela, cv = pos_rela.sc, wv = emb)
neg_rela_dist_centroid_with_dem_seed = CMDist(dtm = dfmat_neg_rela, cv = pos_dem.sc, wv = emb)

```


```{r}
p1=hist(pos_cult_dist_centroid_with_cult_seed[,2])
p2=hist(neg_cult_dist_centroid_with_cult_seed[,2])
plot( p1, col=rgb(0,0,1,1/4), main="Didstribution of positive vs. negative cultural cwmd scores")  # first histogram
plot( p2, col=rgb(1,0,0,1/4), add=T)  # second

legend("topright", c("negative", "positive"), col=c("purple", "red"), lwd=10)

```



```{r}
p1=hist(pos_rela_dist_centroid_with_rela_seed[,2])
p2=hist(neg_rela_dist_centroid_with_rela_seed[,2])
plot( p1, col=rgb(0,0,1,1/4), main="Didstribution of positive vs. negative relational cwmd scores")  # first histogram
plot( p2, col=rgb(1,0,0,1/4), add=T)  # second

legend("topright", c("negative", "positive"), col=c("purple", "red"), lwd=10)

```

```{r}
p1=hist(pos_dem_dist_centroid_with_dem_seed[,2])
p2=hist(neg_dem_dist_centroid_with_dem_seed[,2])
plot( p1, col=rgb(0,0,1,1/4), main="Didstribution of positive vs. negative demographic cwmd scores")  # first histogram
plot( p2, col=rgb(1,0,0,1/4), add=T)  # second

legend("topright", c("negative", "positive"), col=c("purple", "red"), lwd=10)

```



```{r}

neg_cult_sample$cult_cwmd_scores = neg_cult_dist_centroid_with_cult_seed$ceremonial_centroid
neg_cult_sample$dem_cwmd_scores =  neg_cult_dist_centroid_with_dem_seed$competition_centroid
neg_cult_sample$rela_cwmd_scores =  neg_cult_dist_centroid_with_rela_seed$buffer_centroid

```


```{r}

pos_cult_sample$cult_cwmd_scores=pos_cult_dist_centroid_with_cult_seed$ceremonial_centroid
pos_cult_sample$dem_cwmd_scores =  pos_cult_dist_centroid_with_dem_seed$competition_centroid
pos_cult_sample$rela_cwmd_scores =  pos_cult_dist_centroid_with_rela_seed$buffer_centroid

```


```{r}

neg_rela_sample$cult_cwmd_scores= neg_rela_dist_centroid_with_cult_seed$ceremonial_centroid
neg_rela_sample$dem_cwmd_scores =  neg_rela_dist_centroid_with_dem_seed$competition_centroid
neg_rela_sample$rela_cwmd_scores =  neg_rela_dist_centroid_with_rela_seed$buffer_centroid


```


```{r}

pos_rela_sample$cult_cwmd_scores= pos_rela_dist_centroid_with_cult_seed$ceremonial_centroid
pos_rela_sample$dem_cwmd_scores =  pos_rela_dist_centroid_with_dem_seed$competition_centroid
pos_rela_sample$rela_cwmd_scores =  pos_rela_dist_centroid_with_rela_seed$buffer_centroid

```


```{r}

neg_dem_sample$cult_cwmd_scores= neg_dem_dist_centroid_with_cult_seed$ceremonial_centroid
neg_dem_sample$dem_cwmd_scores =  neg_dem_dist_centroid_with_dem_seed$competition_centroid
neg_dem_sample$rela_cwmd_scores =  neg_dem_dist_centroid_with_rela_seed$buffer_centroid


```


```{r}

pos_dem_sample$cult_cwmd_scores= pos_dem_dist_centroid_with_cult_seed$ceremonial_centroid
pos_dem_sample$dem_cwmd_scores =  pos_dem_dist_centroid_with_dem_seed$competition_centroid
pos_dem_sample$rela_cwmd_scores =  pos_dem_dist_centroid_with_rela_seed$buffer_centroid

```




## Normalize scores


```{r}
pos_dem_sample[,c('normalized_cult_cwmd_scores', 'normalized_dem_cwmd_scores', 'normalized_rela_cwmd_scores')] = 1-t(apply(pos_dem_sample[,c('cult_cwmd_scores', 'dem_cwmd_scores', 'rela_cwmd_scores')], 1, function(x)(x-min(x))/(max(x)-min(x))))

neg_dem_sample[,c('normalized_cult_cwmd_scores', 'normalized_dem_cwmd_scores', 'normalized_rela_cwmd_scores')] = 1-t(apply(neg_dem_sample[,c('cult_cwmd_scores', 'dem_cwmd_scores', 'rela_cwmd_scores')], 1, function(x)(x-min(x))/(max(x)-min(x))))
```


```{r}

pos_cult_sample[,c('normalized_cult_cwmd_scores', 'normalized_dem_cwmd_scores', 'normalized_rela_cwmd_scores')] = 1-t(apply(pos_cult_sample[,c('cult_cwmd_scores', 'dem_cwmd_scores', 'rela_cwmd_scores')], 1, function(x)(x-min(x))/(max(x)-min(x))))

neg_cult_sample[,c('normalized_cult_cwmd_scores', 'normalized_dem_cwmd_scores', 'normalized_rela_cwmd_scores')] = 1-t(apply(neg_cult_sample[,c('cult_cwmd_scores', 'dem_cwmd_scores', 'rela_cwmd_scores')], 1, function(x)(x-min(x))/(max(x)-min(x))))

```

```{r}

pos_rela_sample[,c('normalized_cult_cwmd_scores', 'normalized_dem_cwmd_scores', 'normalized_rela_cwmd_scores')] = 1-t(apply(pos_rela_sample[,c('cult_cwmd_scores', 'dem_cwmd_scores', 'rela_cwmd_scores')], 1, function(x)(x-min(x))/(max(x)-min(x))))

neg_rela_sample[,c('normalized_cult_cwmd_scores', 'normalized_dem_cwmd_scores', 'normalized_rela_cwmd_scores')] = 1-t(apply(neg_rela_sample[,c('cult_cwmd_scores', 'dem_cwmd_scores', 'rela_cwmd_scores')], 1, function(x)(x-min(x))/(max(x)-min(x))))

```




```{r}
p1=hist(pos_cult_sample[,'normalized_cult_cwmd_scores'])
p2=hist(neg_cult_sample[,'normalized_cult_cwmd_scores'])
plot( p1, col=rgb(0,0,1,1/4), main="Didstribution of positive vs. negative cultural cwmd scores")  # first histogram
plot( p2, col=rgb(1,0,0,1/4), add=T)  # second

legend("topright", c("negative", "positive"), col=c("purple", "red"), lwd=10)

```

```{r}
p1=hist(pos_dem_sample[,'normalized_dem_cwmd_scores'])
p2=hist(neg_dem_sample[,'normalized_dem_cwmd_scores'])
plot( p1, col=rgb(0,0,1,1/4), main="Didstribution of positive vs. negative demographic cwmd scores")  # first histogram
plot( p2, col=rgb(1,0,0,1/4), add=T)  # second

legend("topright", c("negative", "positive"), col=c("purple", "red"), lwd=10)

```

```{r}
p1=hist(pos_rela_sample[,'normalized_rela_cwmd_scores'])
p2=hist(neg_rela_sample[,'normalized_rela_cwmd_scores'])
plot( p1, col=rgb(0,0,1,1/4), main="Didstribution of positive vs. negative relational cwmd scores")  # first histogram
plot( p2, col=rgb(1,0,0,1/4), add=T)  # second

legend("topright", c("negative", "positive"), col=c("purple", "red"), lwd=10)

```



```{r}

write.csv(pos_cult_sample,'/Users/nancyxu/Desktop/complit/pos_cult_sample_cwmd_df.csv')
write.csv(neg_cult_sample,'/Users/nancyxu/Desktop/complit/neg_cult_sample_cwmd_df.csv')

write.csv(pos_rela_sample,'/Users/nancyxu/Desktop/complit/pos_rela_sample_cwmd_df.csv')
write.csv(neg_rela_sample,'/Users/nancyxu/Desktop/complit/neg_rela_sample_cwmd_df.csv')

write.csv(pos_dem_sample,'/Users/nancyxu/Desktop/complit/pos_dem_sample_cwmd_df.csv')
write.csv(neg_dem_sample,'/Users/nancyxu/Desktop/complit/neg_dem_sample_cwmd_df.csv')
```








